Inferring community characteristics in labelled networks

### 2021-05-13 nips/submission.tex
Scaffold algorithms

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{bbm}
\usepackage{amssymb}

@@

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{algorithmic}
\usepackage{algorithm}

@@

\begin{algorithm} % enter the algorithm environment
	\caption{Block membership sample generation} % give the algorithm a caption
	\label{alg:b-samples} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment

		\FOR{$t \in \{0, 1 \dots T_b - 1\}$}
			\STATE $b' \gets \sim q_b(b^{(t)}, b' | A)$
			\STATE $\log \alpha_b \gets \log \alpha_b(b^{(t)}, b' | A)$
			\STATE $u \gets \sim \textrm{Unif}(0,1)$
			\IF{$\log u < \log \alpha_b$}
				\STATE $b^{(t+1)} \gets b'$
			\ELSE
				\STATE $b^{(t+1)} \gets b^{(t)}$
			\ENDIF
		\ENDFOR

		\STATE \textbf{return} $\{b^{(t)}\}_{t=1}^{T_b}$

	\end{algorithmic}
\end{algorithm}

\begin{algorithm} % enter the algorithm environment
	\caption{LBGM parameter pseudo-marginal inference} % give the algorithm a caption
	\label{alg:theta-samples} % and a label for \ref{} commands later in the document
	\begin{algorithmic} % enter the algorithmic environment

		\STATE $\mathcal{S} \gets \textrm{range}(\textrm{burn-in}, T_b, \textrm{thinning})$
		\STATE $\hat{Y}_{ij} \gets \frac{1}{\mathcal{|S|}} \sum_{t \in \mathcal{S}} \one \{ b^{(t)}_i = j\} \quad \forall i,j$

		\item[]

		\FOR{$t \in \{0, 1 \dots T_\theta - 1\}$}
		\STATE $\theta' \gets \sim q_\theta(\theta^{(t)}, \theta' | X, \hat{Y})$
		\STATE $\log \alpha_\theta \gets \log \alpha_\theta(\theta^{(t)}, \theta' | A, \hat{Y})$
		\STATE $u \gets \sim \textrm{Unif}(0,1)$
		\IF{$\log u < \log \alpha_\theta$}
		\STATE $\theta^{(t+1)} \gets \theta'$
		\ELSE
		\STATE $\theta^{(t+1)} \gets \theta^{(t)}$
		\ENDIF
		\ENDFOR

		\STATE \textbf{return} $\{\theta^{(t)}\}_{t=1}^{T_\theta}$

	\end{algorithmic}
\end{algorithm}
